E1 Testing - Bayesian Mixed Models

### 2023-08-13 Analysis/e1_brms_test.qmd
indv difference plots

@@

@@

@@

>>>>

individual_coefs <- coef(gt_vx)$id %>%
    as_tibble(rownames = "id") %>%
    select(id, starts_with("Estim")) %>%
    pivot_longer(cols = -id, names_to = "variable", values_to = "value") %>%
    separate(variable, c("type", "effect"), sep = "\\.")

@@

mcmc_hist(e1_testDistRF2_0,prob=.5,regex_pars=c("^r_id\\[1,.*\\]"))

@@

bform1 <- bf(mvbind(vx, dist) ~ condit * vb + (1|p|id)) + set_rescor(TRUE)
mv1 <- brm(bform1, data = test, chains = 2, cores = 2)

conditional_effects(mv1)
pp_check(mv1,resp="dist")
pp_check(mv1,resp="vx")

ppc_dens_overlay_grouped(test$vx,posterior_predict(mv1,ndraws=200),test$vb)
bayes_R2(mv1)

bf_dist <- bf(dist|trunc(lb=-70) ~ condit * vb + (0 + vb|id) ) + gaussian()
bf_vx <- bf(vx|trunc(lb=0) ~ condit * vb + (0 + vb|id)) + gaussian()

mv3 <- brm(bf_dist + bf_vx + set_rescor(FALSE),
            data = test, chains = 2, cores = 2,iter=1300, silent=0,
           file=here::here("data/model_cache/mv_trunc2"))
bayes_R2(mv3)
pp_check(mv3,resp="dist")

ppc_dens_overlay_grouped(test$vx,posterior_predict(mv3,ndraws=200),test$vb)

bform2 <- bf(mvbind(vx, vy) ~ condit * vb + (0+vb|id)) + set_rescor(FALSE)
mv3 <- brm(bform2, data = test, chains = 2, cores = 2,silent=0)
bayes_R2(mv3)
pp_check(mv3,resp="vx")
pp_check(mv3,resp="vy")

fitted(mv3) %>%
  as_tibble() %>%
  bind_cols(test %>% select(id,condit,vx,vy,vb,bandInt)) %>%
  ggplot(aes(x = vx, y = Estimate.vx)) +
  geom_abline(linetype = 2, color = "grey50", linewidth = .5) +  
  geom_point(size = 1.5, aes(color=), alpha = 3/4) +
  geom_linerange(aes(ymin = Q2.5.vx, ymax = Q97.5.vx),
                 size = 1/4, color = "firebrick4") +
  facet_wrap(~vb)

@@

vx_mm4 <- brm(vx ~ (1+vb|id), data=test,chains=2,silent=0)

mcmc_areas(vx_mm4,prob=.5,regex_pars=c("^r_id\\[1,.*\\]"),regex=T)

vx_mm5<- brm(vx ~ 0 + (0+vb|id), data=test,chains=2,silent=0,iter=1200)
mcmc_areas(vx_mm5,prob=.5,regex_pars=c("^r_id\\[1,.*\\]"),regex=T)

mcmc_areas(vx_mm5,prob=.5,regex_pars=c("^r_id\\[2,.*\\]"),regex=T)

mcmc_areas(vx_mm5,prob=.5,regex_pars=c("^r_id\\[3,.*\\]"),regex=T) +
  geom_point(size=.1,alpha=.4)+ggtitle("test")

plot_subject_fits <- function(model, subject_code) {
  pattern <- glue("^r_id\\[{subject_code},.*\\]")
  plot <- mcmc_areas(model, prob = .5, regex_pars = c(pattern)) +
            ggtitle(glue("fit for subject #{subject_code}:"))
  return(plot)
}

plot_subject_fits(vx_mm5,86)
